THESIS PROJECT PROPOSAL

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

It is proposed to study the production channel of the Higgs boson associated with a single top quark in the Large Hadron Collider of the 
CERN laboratory. The measurement of this process complements other measurements of the yukawa coupling parameter of the top quark and 
Higgs boson. It is a part of the physics program of CMS international collaborations and ATLAS and it has not been observed so far. It is proposed to study sensitivity with the current data in the channel where the events are identified with two muons of the same sign. The impact of uncertainties will be studied and projections will be made to the future phases of the LHC.

>>>>

In this project, it is proposed to study the production channel of the Higgs boson associated with a single top quark in the Large Hadron Collider of the CERN laboratory. The measurement of this process complements other measurements of the yukawa coupling parameter of the top quark and Higgs boson. It is a part of the physics program of CMS international collaborations and ATLAS and it has not been observed so far. It is proposed to study sensitivity with the current data in the channel where the events are identified with two muons of the same sign. The impact of uncertainties will be studied and projections will be made to the future phases of the LHC. For these studies the data of the run two (2015-2018) of the LHC identifying the signal events with two muons from the same sign. It is also expected to estimate projections for the high brightness phase of the LHC (HL-LHC) that began in 2026.
